---
title: "analysis_tss_experiment_1123"
author: "Wonyoung So"
date: "11/23/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(foreign)
require(tidyverse)
require(rdrobust)
require(stargazer)
require(httr)
require(jsonlite)
require(ggplot2)
require(dplyr)
require(miceadds)
library(miceadds)
require(texreg)
library(sandwich)
library(lmtest)
library(nnet)
library(modelsummary)
library(estimatr)
```

## Import Data

```{r importdata, include=FALSE, message = FALSE}}
tss_df <- fromJSON("./mturk_landlords_decisions_06-2021.json")
```

```{r meancentering}

tss_df <- tss_df %>% mutate(yesno = ifelse(accept_type == "No", 0, 1))
tss_df <- tss_df %>% 
  mutate(security_deposit2 = ifelse(is.na(security_deposit), 0, security_deposit))

tss_df$view_mode <- as.factor(tss_df$view_mode)
tss_df$view_mode <- relevel(tss_df$view_mode, ref="Type 1")

tss_df$score <- as.factor(tss_df$score)
tss_df$score <- relevel(tss_df$score, ref="LOW - CLEAN")

tss_df_centered <- tss_df

# linearize and standardized income
tss_df_centered <- tss_df_centered %>% 
  mutate(income_linear = 
    case_when(
      income == 'Under $40,000' ~ log(40000),
      income == '$40,001-$60,000' ~ 50000,
      income == '$60,001-$80,000' ~ 70000,
      income == '$80,001-$100,000' ~ 90000,
      income == '$100,001-$120,000' ~ 110000,
      income == 'More than $120,000' ~ 120000
    ))

tss_df_centered$income_stdzd <- scale(tss_df_centered$income_linear)

# landlords okay_blanket_policy + number_of_unit + race_ethnicity + gender + income_linear

# first, factorize them

# okay blanket policy's reference category = no
tss_df_centered <- tss_df_centered %>%
  mutate(okay_blanket_policy_yes =
           ifelse(okay_blanket_policy == "Yes", 1, 0)) 

# number_of_units: reference category: 1 unit.
tss_df_centered <- tss_df_centered %>% 
  mutate(
    nou_2_4_units =
      ifelse(number_of_unit == "2-4 units", 1, 0),
    nou_4_10_units =
      ifelse(number_of_unit == "4-10 units", 1, 0),
    nou_10_50_units =
      ifelse(number_of_unit == "10-50 units", 1, 0),
    nou_50_units =
      ifelse(number_of_unit == "More than 50 units", 1, 0)
  )

# race_ethnicity: reference category: white
tss_df_centered <- tss_df_centered %>% 
  mutate(
    race_asian =
      ifelse(race_ethnicity == "Asian", 1, 0),
    race_black =
      ifelse(race_ethnicity == "Black", 1, 0),
    race_hispanic =
      ifelse(race_ethnicity == "Hispanic", 1, 0),
    race_native =
      ifelse(race_ethnicity == "Native American", 1, 0),
    race_other =
      ifelse(race_ethnicity == "Other", 1, 0)
  )

# gender: reference category: male
tss_df_centered <- tss_df_centered %>% 
  mutate(
    gender_female =
      ifelse(gender == "Female", 1, 0)
  )

# covariate centering
tss_df_centered$income_linear_cent <- tss_df_centered$income_stdzd -
  mean(tss_df_centered$income_stdzd)

tss_df_centered$okay_blanket_policy_yes_cent <- tss_df_centered$okay_blanket_policy_yes -
  mean(tss_df_centered$okay_blanket_policy_yes)

tss_df_centered$nou_2_4_units_cent <- tss_df_centered$nou_2_4_units -
  mean(tss_df_centered$nou_2_4_units)

tss_df_centered$nou_4_10_units_cent <- tss_df_centered$nou_4_10_units -
  mean(tss_df_centered$nou_4_10_units)

tss_df_centered$nou_10_50_units_cent <- tss_df_centered$nou_10_50_units -
  mean(tss_df_centered$nou_10_50_units)

tss_df_centered$nou_50_units_cent <- tss_df_centered$nou_50_units -
  mean(tss_df_centered$nou_50_units)

tss_df_centered$race_asian_cent <- tss_df_centered$race_asian -
  mean(tss_df_centered$race_asian)

tss_df_centered$race_black_cent <- tss_df_centered$race_black -
  mean(tss_df_centered$race_black)

tss_df_centered$race_hispanic_cent <- tss_df_centered$race_hispanic -
  mean(tss_df_centered$race_hispanic)

tss_df_centered$race_native_cent <- tss_df_centered$race_native -
  mean(tss_df_centered$race_native)

tss_df_centered$race_other_cent <- tss_df_centered$race_other -
  mean(tss_df_centered$race_other)

tss_df_centered$gender_female_cent <- tss_df_centered$gender_female -
  mean(tss_df_centered$gender_female)

# final landlord-level covariates:
# income_linear_cent + okay_blanket_policy_yes_cent + nou_2_4_units_cent + nou_4_10_units_cent + nou_10_50_units_cent + nou_50_units_cent + race_asian_cent + race_black_cent + race_hispanic_cent + race_native_cent + race_other_cent + gender_female_cent

tss_df_centered
```


## Rental decision Logistic Regression

```{r}

# without covariates - all
model_1 <- glm(data = tss_df_centered, formula = yesno ~ view_mode * score, family = "binomial")
model_1_rob <- coeftest(model_1, vcov. = vcovCL(model_1,  cluster=tss_df_centered$user_id, type ="HC2"))

pR2_model_1 <- 1 - model_1$deviance / model_1$null.deviance
pR2_model_1

stargazer(model_1_rob, type = "text")
#+  nou_2_4_units_cent + nou_4_10_units_cent + nou_10_50_units_cent + nou_50_units_cent + race_asian_cent + race_black_cent + race_hispanic_cent + race_native_cent + race_other_cent + gender_female_cent

# with covariates - all
model_2 <- glm(data = tss_df_centered, formula = yesno ~ view_mode * score + nou_10_50_units_cent, family = "binomial")

pR2_model_2 <- 1 - model_2$deviance / model_2$null.deviance
pR2_model_2

model_2_rob <- coeftest(model_2, vcov. = vcovCL(model_2, cluster=tss_df_centered$user_id))


stargazer(model_1_rob, model_2_rob, type = "text",
          add.lines = list(c("neg2ll", round(c(model_1$deviance, model_2$deviance), 2)),
                           c("r2pseudo", round(unlist(lapply(list(model_1, model_2), FUN = function(x) 1 - x$deviance/x$null.deviance)), 4))))
anova(model_1, model_2, test="LRT")

```
# without covariates - evictions
nrow(eviction_tss_df)
eviction_tss_df <- tss_df_centered %>% filter(report_type == "Eviction")
eviction_tss_df$score <- relevel(eviction_tss_df$score, ref="MID")
model_3 <- glm(data = eviction_tss_df, formula = yesno ~ view_mode * score, family = "binomial")
model_3_rob <- coeftest(model_3, vcov. = vcovCL(model_3,  cluster=eviction_tss_df$user_id, type ="HC2"))

pR2_model_3 <- 1 - model_3$deviance / model_3$null.deviance
pR2_model_3

stargazer(model_3_rob, type = "text")



# with covariates - evictions
model_4 <- glm(data = eviction_tss_df, formula = yesno ~ view_mode * score + income_linear_cent + okay_blanket_policy_yes_cent + nou_2_4_units_cent + nou_4_10_units_cent + nou_10_50_units_cent + nou_50_units_cent + race_asian_cent + race_black_cent + race_hispanic_cent + race_native_cent + race_other_cent + gender_female_cent, family = "binomial")

pR2_model_4 <- 1 - model_4$deviance / model_4$null.deviance
pR2_model_4

model_4_rob <- coeftest(model_4, vcov. = vcovCL(model_4, cluster=eviction_tss_df$user_id))

stargazer(model_4_rob, type = "text")



# without covariates - criminal records
criminal_tss_df <- tss_df_centered %>% filter(report_type == "Criminal")
criminal_tss_df$score <- relevel(criminal_tss_df$score, ref="MID")
model_5 <- glm(data = criminal_tss_df, formula = yesno ~ view_mode * score, family = "binomial")
model_5_rob <- coeftest(model_5, vcov. = vcovCL(model_5,  cluster=criminal_tss_df$user_id, type ="HC2"))

pR2_model_5 <- 1 - model_5$deviance / model_5$null.deviance
pR2_model_5

stargazer(model_5_rob, type = "text")



# with covariates - criminal records
model_6 <- glm(data = criminal_tss_df, formula = yesno ~ view_mode * score + income_linear_cent + okay_blanket_policy_yes_cent + nou_2_4_units_cent + nou_4_10_units_cent + nou_10_50_units_cent + nou_50_units_cent + race_asian_cent + race_black_cent + race_hispanic_cent + race_native_cent + race_other_cent + gender_female_cent, family = "binomial")

pR2_model_6 <- 1 - model_5$deviance / model_5$null.deviance
pR2_model_6

model_6_rob <- coeftest(model_6, vcov. = vcovCL(model_6, cluster=criminal_tss_df$user_id))

stargazer(model_6_rob, type = "text")

```

## Security Deposit OLS

```{r}

library(fixest)
tss_df_sd <- tss_df_centered %>% filter(accept_type == "Yes with security deposit")
nrow(tss_df_sd)
model_7 <- feols(security_deposit ~ view_mode * score, data = tss_df_sd, cluster = ~user_id)
etable(model_7)

model_8 <- feols(security_deposit ~ view_mode * score + income_linear_cent + okay_blanket_policy_yes_cent + nou_2_4_units_cent + nou_4_10_units_cent + nou_10_50_units_cent + nou_50_units_cent + race_asian_cent + race_black_cent + race_hispanic_cent + race_native_cent + race_other_cent + gender_female_cent, data = tss_df_sd, cluster = tss_df_sd$user_id)
etable(model_8)


tss_df_sd_eviction <- tss_df_sd %>% filter(report_type == "Eviction")
nrow(tss_df_sd_eviction)
model_9 <- feols(security_deposit ~ view_mode * score, data = tss_df_sd_eviction, cluster = ~user_id)
etable(model_9)

model_10 <- feols(security_deposit ~ view_mode * score + income_linear_cent + okay_blanket_policy_yes_cent + nou_2_4_units_cent + nou_4_10_units_cent + nou_10_50_units_cent + nou_50_units_cent + race_asian_cent + race_black_cent + race_hispanic_cent + race_native_cent + race_other_cent + gender_female_cent, data = tss_df_sd_eviction, cluster = ~user_id)
etable(model_10)

## OLS criminal

tss_df_sd_criminal <- tss_df_sd %>% filter(report_type == "Criminal")
tss_df_sd_criminal$score <- relevel(tss_df_sd_criminal$score, ref="MID")
nrow(tss_df_sd_criminal)
model_11 <- feols(security_deposit ~ view_mode * score, data = tss_df_sd_criminal, cluster = ~user_id)
etable(model_11)

model_12 <- feols(security_deposit ~ view_mode * score | user_id, data = tss_df_sd_criminal, cluster = ~user_id)

model_12_1 <- lm(security_deposit ~ view_mode * score + income_linear_cent + okay_blanket_policy_yes_cent + nou_2_4_units_cent + nou_4_10_units_cent + nou_10_50_units_cent + nou_50_units_cent + race_asian_cent + race_black_cent + race_hispanic_cent + race_native_cent + race_other_cent + gender_female_cent, data = tss_df_sd_criminal)

model_12_1 %>% summary()
etable(model_12)
model_12

```

## Analysis of reports that have eviction records

```{r eviction record analysis}

tss_df_centered %>% filter(report_type == "Criminal") %>% count()
tss_df_centered %>% filter(report_type == "Eviction") %>% count()


tss_df_centered %>% filter(score == "MID" | score == "HIGH") %>% count()
tss_df_centered %>% filter(score == 'LOW - CLEAN') %>% count()

nrow(tss_df_centered)
```


## power calculation

```{r}
library(pwr)

pwr.f2.test(u = 21, f2=0.15, sig.level = 0.05, power = 0.8)

137 + 21 + 1
```






```{r}
logit2prob <- function(logit){
  odds <- exp(logit)
  prob <- odds / (1 + odds)
  return(prob)
}

1.326 / (1 + 1.326)
exp(1.326)

logit2prob(1.326)
```



## Yes - No Linear Probability Model

```{r}
model_1 <- lm_robust(data = tss_df_centered, formula = yesno ~ view_mode * score, cluster=tss_df_centered$user_id, se_type='CR2')
model_1 %>% summary()

logit_wo_cluster <- miceadds::glm.cluster(data = tss_df_centered, formula = yesno ~ view_mode * score + okay_blanket_policy + number_of_unit + race_ethnicity + gender + income, cluster="user_id", family = "binomial")

```